### 2016-07-25 syntax.tex
cheers

\heading{Examples.}
It is not hard to see Bloom filters are one possible instantiation a set-representation primitive.
Fix an $n \geq 0$, let $\mathcal{S}=[\univ]^n$, and fix $\Sigma=\bits$.  
Next, let $\calQ$ be a set of predicates $q_x$, one for each $x \in \univ$,
such that $q_x(S)=1$ iff $x \in S$.  Define algorithm~$\Rep$, with integers $k, m > 0$ and a description of a hash function family~$\mathcal{H}=\{h \colon \univ \to \{1,2,\ldots,m\}\}$ hardwared into it, to sample hash functions $h_1, \ldots, h_k$ from~$\mathcal{H}$ and then computes an $m$-bit array in the standard way. It sets $\aux = (h_1, \ldots, h_k)$ and $M$ to be the bit array, and returns these.  The algorithm~$\Qry$ is defined so that, on input $(M,\aux,q_x)$, it returns 1 iff $M[h_1(x)]=1 \wedge M[h_2(x)]=1 \wedge \cdots \wedge M[h_k(x)]=1$ holds.
  %\tsnote{If $\mathcal{Q}=U$ and we use the
%  semantics you suggest, then isn't Equation~\ref{eqn:correctness}
%  both correctness and soundness?  If so, I don't see how this
%  captures the classical BF, which requires $\epsilon=0$ for one kind
%  of error, but allows $\epsilon>0$ for the other. } 
%\jnote{The definition does not distinguish
%  between elements in the set (for which $q(S)=1$) or outside the set (for which
%  $q(S)=0$). But a Bloom filter does satisfy Equation~\ref{eqn:correctness} in either case.}
%  \jnote{In that sense, I am using ``soundness'' and ``correctness'' interchangeably here.}
%  \jnote{I'm not tied to allowing false negatives when we specialize the definition to the case
%  of set-membership queries. But in the abstract definition it seems unclear why one would choose
%  some queries on which error is ok and other queries where error is not allowed. Though if one
%  wanted to be general, one could simply have two (disjoint) sets of queries $\mathcal{Q}_1, \mathcal{Q}_2$
%  where error is allowed on the former but not on the latter.}
We note that while our correctness condition does not distinguish among types of errors, it also does not preclude instantiations (like the classical Bloom filter) that admit only one type of error, e.g. false-positives.

>>>>

\heading{Examples.}
It is not hard to see Bloom filters are one possible instantiation a set-representation primitive.
Fix an $n \geq 0$, let $\mathcal{S}=[\univ]^n$, and fix $\Sigma=\bits$.  
Next, let $\calQ$ be a set of predicates $q_x$, one for each $x \in \univ$,
such that $q_x(S)=1$ iff $x \in S$.  Define algorithm~$\Rep$, with functions $k=k(|S|), m=m(|S|)$ and a description of a hash function family~$\mathcal{H}=\{h \colon \univ \to \{1,2,\ldots,m\}\}$ hardwired into it, to sample hash functions $h_1, \ldots, h_k$ from~$\mathcal{H}$ and then computes an $m$-bit array in the standard way. It sets $\aux = (h_1, \ldots, h_k)$ and $M$ to be the bit array, and returns these.  The algorithm~$\Qry$ is defined so that, on input $(M,\aux,q_x)$, it returns 1 iff $M[h_1(x)]=1 \wedge M[h_2(x)]=1 \wedge \cdots \wedge M[h_k(x)]=1$ holds.
  %\tsnote{If $\mathcal{Q}=U$ and we use the
%  semantics you suggest, then isn't Equation~\ref{eqn:correctness}
%  both correctness and soundness?  If so, I don't see how this
%  captures the classical BF, which requires $\epsilon=0$ for one kind
%  of error, but allows $\epsilon>0$ for the other. } 
%\jnote{The definition does not distinguish
%  between elements in the set (for which $q(S)=1$) or outside the set (for which
%  $q(S)=0$). But a Bloom filter does satisfy Equation~\ref{eqn:correctness} in either case.}
%  \jnote{In that sense, I am using ``soundness'' and ``correctness'' interchangeably here.}
%  \jnote{I'm not tied to allowing false negatives when we specialize the definition to the case
%  of set-membership queries. But in the abstract definition it seems unclear why one would choose
%  some queries on which error is ok and other queries where error is not allowed. Though if one
%  wanted to be general, one could simply have two (disjoint) sets of queries $\mathcal{Q}_1, \mathcal{Q}_2$
%  where error is allowed on the former but not on the latter.}
We note that while our correctness condition does not distinguish among types of errors, it also does not preclude instantiations (like the classical Bloom filter) that admit only one type of error, e.g. false-positives.
